---
title: "p8105_hw1_jkh2157"
output: github_document
date: "2025-09-16"
---

```{r}
library(moderndive)
library(tidyverse)
```

Let's load the early january weather data set 

```{r}
data("early_january_weather")
```

The `early_january_weather` dataset contains **`r nrow(early_january_weather)`** hourly observations and **`r ncol(early_january_weather)`** variables collected at Newark Airport (EWR) in early January 2013.  

Important variables include:  
- `temp`: temperature in °F (mean value: **`r round(mean(early_january_weather$temp, na.rm = TRUE), 1)`** °F)  
- `humid`: relative humidity (%)  
- `time_hour`: timestamp for each hourly measurement  

Now I am going to create a scatterplot for temperature v time_hour 

```{r}
ggplot(early_january_weather, aes(x=time_hour,y=temp, color=humid)) + geom_point()
ggsave("early_january_weather.pdf", height = 4, width = 6)
```

The scatter plot shows that the temperature generally increased over the two week period, and that it fluctuated throughout the day (colder ar night and hotter during the day). Colder temperatures are usually associated with lower humidity and higher temperatures are usually associated with higher humidity. 

Now I am going to create data frames for problem 2 

```{r}
df = tibble (
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0, 
  vec_char = sample (letters, 10),
  vec_factor = factor(sample(c("A","B","C"),10, replace=TRUE))
)
```

