---
title: "p8105_hw1_jkh2157"
output: github_document
date: "2025-09-16"
---

```{r}
library(moderndive)
library(tidyverse)
```

## **Problem 1**

Let's load the early january weather data set 

```{r}
data("early_january_weather")
```

The `early_january_weather` dataset contains **`r nrow(early_january_weather)`** hourly observations and **`r ncol(early_january_weather)`** variables collected at Newark Airport (EWR) in early January 2013.  

Important variables include:  

- `temp`: temperature in °F (mean value: **`r mean(pull(early_january_weather,temp))`** °F) 

- `humid`: relative humidity (%)  

- `time_hour`: timestamp for each hourly measurement  

Now I am going to create a scatter plot for temperature v time hour 

```{r}
ggplot(early_january_weather, aes(x=time_hour,y=temp, color=humid)) + geom_point()
ggsave("early_january_weather.pdf", height = 4, width = 6)
```

The scatter plot shows that the temperature generally increased over the two week period, and that it fluctuated throughout the day (colder ar night and hotter during the day). Colder temperatures are usually associated with lower humidity and higher temperatures are usually associated with higher humidity. 

## **Problem 2**

Now I am going to create data frames for problem 2 

```{r}
df = tibble (
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0, 
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_factor = factor(c("Red","Blue","Green","Red","Blue","Green","Red","Blue","Green","Red"))
)
```

I'm going to run the df variable to check outputs

```{r}
df
```


Now we are going to attemp to take the means 

```{r}
mean(pull(df,vec_numeric))
mean(pull(df,vec_logical))
mean(pull(df,vec_char))
mean(pull(df,vec_factor))
```

When taking the means, it only worked for the numeric and logical vectors but not the character or factor vectors. 

Finally, we will write a chunk of code that applies the as.numeric function to the logical, character, and factor variables. 

```{r, eval=FALSE}
as.numeric(pull(df, vec_logical))
as.numeric(pull(df, vec_char))
as.numeric(pull(df,vec_factor))
```

Using the as.numeric function did clarify why some means worked and why the others did not. It showed that the logical values were 0s (false) and 1s (true), which explains why we were able to get the mean. The character variable was not able to be converted to numeric values, which explains why taking the mean did not work. It also worked for the factor variable because it revealed the integer codes for the different levels. 
